PANCHANGE_data_preprocessing

### 2020-11-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
Fixed some minor errors for NBR cohort

# Specify cohort
```{r Specify cohort}
GLAD = TRUE
EDGI = TRUE
NBR = FALSE
RAMP = FALSE
GLAD_and_EDGI = TRUE
```

@@

```{r source file path}
#source raw data directory: data.raw_path
source("/Users/alishpalmos/Documents/GitHub//PANCHANGE_raw_path.R")
```

>>>>

# Specify cohort
```{r Specify cohort}
GLAD = FALSE
EDGI = FALSE
NBR = TRUE
RAMP = FALSE
GLAD_and_EDGI = FALSE
```

@@

```{r source file path}
#source raw data directory: data.raw_path
source("..//PANCHANGE_raw_path.R")
```
